---
title: "R Plots"
author: "Gustavo Reyes"
date: '2022-05-03'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(forcats)


#setwd("C:/Users/gareyes3/Box/CPS Project- Farm to Facility/Papers/CSV Data/Review 2")
setwd("C:/Users/reyes/Box Sync/CPS Project- Farm to Facility/Papers/CSV Data/Review 2")
#setwd("C:/Users/gareyes3/Box/CPS Project- Farm to Facility/Papers/CSV Data")
#setwd("C:/Users/Gustavo Reyes/Box/CPS Project- Farm to Facility/Papers/CSV Data/Review 2")
```

Contamination progression around the system.

This chunks creates the plot that shows progression through the system as interventions get applied.
Used to get the efficacy of each individual intervention. 


##Powers
```{r}
Powers_df<-read_csv("PowersR2.csv")

Powers_df$ContS<-str_replace("Random Uniform Unclustered", string = Powers_df$ContS, replacement = "Random Uniform (Widespread 100% Cluster)")


Powers_df<- Powers_df %>%
  filter(Type != "None")

Powers_df$Type<-factor(Powers_df$Type, levels = c("PHS4D" ,"PHS4H", "PHSInt", "HS", "RS", "FPS", "CS"))
Powers_df$variable<-factor(Powers_df$variable, levels = c("No Intervention","All Intervention","No Holding","No Precooling", "No Prewash","No Washing","No Sanitation" ))
Powers_df$ContS<-factor(Powers_df$ContS, levels = c("Random Uniform (Widespread 100% Cluster)", "10% Cluster", "1% Cluster"))

Powers_df %>% 
  ggplot(aes(x = Type, y = value, group = variable, fill = variable))+
  #geom_col(position = position_dodge())+
  geom_line( position = position_dodge(width = 0) ,size = 1, alpha = 0.5, aes(color = variable))+
  geom_point(size = 3, position = position_dodge(width = 0),shape = 21) +
  facet_grid(variable~ContS)+
  theme_bw()+
  labs(y = "Sampling Plan Power", x = "Sampling Stage")

ggsave("Powers.tiff", width = 35, height = 22, units = "cm", dpi = 600)

Powers_df %>% 
  ggplot(aes(x = Type, y = value, group = ContS, fill = ContS))+
  #geom_col(position = position_dodge())+
  geom_line( position = position_dodge(width = 0) ,size = 1, alpha = 0.5, aes(color = ContS))+
  geom_point(size = 3, position = position_dodge(width = 0),shape = 21) +
  facet_wrap(~variable)+
  theme_bw()+
  labs(y = "Sampling Plan Power", x = "Sampling Stage")
ggsave("Powers2.tiff", width = 35, height = 22, units = "cm", dpi = 600)


Powers_df %>% 
  ggplot(aes(x = Type, y = value, group = variable, fill = variable))+
  #geom_col(position = position_dodge())+
  geom_line( position = position_dodge(width = 0) ,size = 0.7, alpha = 0.5, aes(color = variable))+
  geom_point(size = 2, position = position_dodge(width = 0),shape = 21) +
  facet_wrap(~ContS)+
  theme_bw()+
  scale_y_continuous(labels = scales::percent)+
  labs(y = "Sampling Plan Power", x = "Sampling Stage", fill = "Process System", color =  "Process System")+
  theme(text = element_text(size=7))+
  theme(legend.key.size = unit(0.8,"line"))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave("Figure 4 - Powers.tiff", width = 6.8, height = 3.7, units = "in", dpi = 300)
ggsave("Figure 4 - Powers.jpeg", width = 6.8, height = 3.7, units = "in", dpi = 300)


```


## Contmainationation progression
```{r}
NI_1_ProgInt<-read_csv("Melted_Prog_DF_NI_1-R2T.csv")
NI_2_ProgInt<-read_csv("Melted_Prog_DF_NI_2-R2T.csv")
NI_3_ProgInt<-read_csv("Melted_Prog_DF_NI_3-R2T.csv")

order_progression<-unique(NI_1_ProgInt$variable) #getting exact order of events

#Function for Calculating the 95% confidence interval for the means.
margin_calc<-function(x){
  margin <- qt(0.975,df=1000-1)*sd(x)/sqrt(1000)
}

#random
NI_Summ<-NI_1_ProgInt %>% 
  group_by(Type,variable ) %>% 
  summarize(mean= mean(value),h95 =mean + margin_calc(value),l95 =mean - margin_calc(value)) %>% 
  mutate(ContScen = "Random Uniform (Widespread 100% Cluster)") %>% 
  drop_na()
#10%
NI_Summ_3<-NI_3_ProgInt %>% 
  group_by(Type,variable ) %>% 
  summarize(mean= mean(value),h95 =mean + margin_calc(value),l95 =mean - margin_calc(value)) %>% 
  mutate(ContScen = "10% Clustered Contamination") %>% 
  drop_na()
#1%
NI_Summ_2<-NI_2_ProgInt %>% 
  group_by(Type,variable ) %>% 
  summarize(mean= mean(value),h95 =mean + margin_calc(value),l95 =mean - margin_calc(value)) %>% 
    mutate(ContScen = "1% Clustered Contamination") %>% 
  drop_na()

#Getting Summary Stats. for intervention effect. 
#log changes.
1.59e+3

NI_Summ %>% 
  filter(variable == "After CS Samp") %>% 
  mutate(logchange= log10(mean/1.59e+3),
         logchange95l = log10(h95/1.59e+3),
         logchange95h = log10(l95/1.59e+3)
         )

Binded_all<-bind_rows(NI_Summ,NI_Summ_3,NI_Summ_2)

#Updating Intervention Names: 
Binded_all$Type<-str_replace("BaselineAI", string = Binded_all$Type, replacement = "Baseline All-Intervention")
Binded_all$Type<-str_replace("BaselineNI", string = Binded_all$Type, replacement = "Baseline No-Intervention")
Binded_all$Type<-str_replace("Holding", string = Binded_all$Type, replacement = "Preharvest Holding")
Binded_all$Type<-str_replace("PreSpray_Wash", string = Binded_all$Type, replacement = "Prewash")
Binded_all$Type<-str_replace("Washing", string = Binded_all$Type, replacement = "Washing")

#fixing the word preharvest
Binded_all$variable<-str_replace("Pre-Harvest", string = Binded_all$variable, replacement = "Preharvest")
order_progression2<-str_replace("Pre-Harvest", string = order_progression, replacement = "Preharvest")

Binded_all$variable<-factor(Binded_all$variable, levels=order_progression2)
Binded_all$ContScen<-str_replace("Random Contamination", string = Binded_all$ContScen, replacement = "Random unclustered")
Binded_all$ContScen<-factor(Binded_all$ContScen, levels=c("Random Uniform (Widespread 100% Cluster)","10% Clustered Contamination","1% Clustered Contamination"))

Binded_all$Type<-factor(Binded_all$Type, levels=c("Baseline No-Intervention", "Baseline All-Intervention","Preharvest Holding", "Precooling", "Prewash", "Washing", "Sanitation" ))


ggplot(data= Binded_all, aes(x= variable,y = mean, group= Type, color = Type, linetype=Type, fill = Type))+
  geom_line(size = 0.3)+
  geom_ribbon(aes(ymin = l95, ymax = h95), alpha = 0.2, size = 0.3)+
   scale_y_continuous(trans='log10',
                      labels = trans_format("log10", math_format(10^.x)))+
  labs(y= "Total Adulterant Cells in System", x="Process Stage")+
  #ggtitle("1) Random Contamination")+
  facet_wrap(~ ContScen, ncol = 3)+
  labs(color = "Interventions", fill = "Interventions", linetype = "Interventions")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  theme(text = element_text(size=7))+
  theme(legend.key.size = unit(1,"line"))


ggsave("Figure 3-Contamination_Progression.tiff", width = 6.8, height = 3.7, units = "in", dpi = 300)
ggsave("Figure 3-Contamination_Progression.jpeg", width = 6.8, height = 3.7, units = "in", dpi = 300)


```


## Factor Sensitivity plot

```{r}
FSdf<-read_csv("FSdf-Final-1-5.csv")
```

```{r}
order_x = c("Baseline-NI",
            "Baseline-NI-Washing",
            "Baseline-NI-Washing 10 ppm",
            "Baseline-NI Holding",
            "Baseline-NI Pre-cooling", 
            "Baseline-NI PreWash",
            "Baseline-NI Sanitation", 
            "Baseline-NI PHS4d",
            "Baseline-NI PHS4h",
            "Baseline-NI Int",
            "Baseline-NI HS", 
            "Baseline-NI RS",
            "Baseline-NI FPS", 
            "Baseline-NI CS", 
            "Baseline-AI",
            "Baseline-AI PHS4d",
            "Baseline-AI PHS4h", 
            "Baseline-AI PHSInt", 
            "Baseline-AI HS",
            "Baseline-AI RS", 
            "Baseline-AI FPS", 
            "Baseline-AI CS")

labels_x = c("Baseline-NI" = "Baseline",
            "Baseline-NI-Washing" = "Washing",
            "Baseline-NI-Washing 10 ppm" = "Washing 10 ppm",
            "Baseline-NI Holding" ="Holding",
            "Baseline-NI Pre-cooling" = "Pre-Cooling", 
            "Baseline-NI PreWash" = "Pre-Wash",
            "Baseline-NI Sanitation" = "Sanitation", 
            "Baseline-NI PHS4d" = "PHS 4d",
            "Baseline-NI PHS4h"="PHS 4h",
            "Baseline-NI Int" = "PHS Int",
            "Baseline-NI HS" = "HS", 
            "Baseline-NI RS" = "RS",
            "Baseline-NI FPS" = "FPS", 
            "Baseline-NI CS" = "CS", 
            "Baseline-AI"= "All Interventions",
            "Baseline-AI PHS4d" = "PHS 4d",
            "Baseline-AI PHS4h"="PHS 4h", 
            "Baseline-AI PHSInt" = "PHS Int", 
            "Baseline-AI HS"= "HS",
            "Baseline-AI RS" = "RS", 
            "Baseline-AI FPS" = "FPS", 
            "Baseline-AI CS" = "CS")



FSdf$System<-c(rep("No Intervention", 14),rep("All Interventions", 8))

hline_data <- data.frame(y = c(0, -3.4), Baseline_System = factor(c("No Intervention", "All Intervention")), 
                         stringsAsFactors = FALSE)

pfs = ggplot(data= FSdf, aes(x = fct_reorder(Name, abs(FS)), y = FS, fill = System))+
  geom_col()+
  coord_flip()


  pfs+
  theme(text = element_text(size=24))+
  #geom_hline(yintercept = -3.492672,linetype="dotted", size = 2)+
  # geom_hline(yintercept = 0,linetype="dashed",size = 2)+
  ylab("Factor Sensitivity Index")+
  xlab("Scenario or Intervention")+
  scale_x_discrete(labels = labels_x)+
  theme(text = element_text(size=26), axis.text = element_text(size = 26))+
  theme(legend.text=element_text(size=18),legend.title=element_text(size=18))+
  #scale_x_discrete(limits=rev)+
  geom_hline(data = hline_data, 
       aes(yintercept = y, linetype = Baseline_System),size =2)+
  ggtitle("Factor Sensitivity Analysis (FS)")+
    scale_linetype_manual(values = c("No Intervention" = "dotted", "All Intervention" = "dashed"), 
                        name = "")

  ggsave("FS-Final.png", width = 40, height = 30, units = "cm", dpi = 300)
  
  
##NEW###

FSdf$System <-str_replace("Baseline NI", string = FSdf$System, replacement = "Baseline No-Intervention")
FSdf$System <-str_replace("Baseline  AI", string = FSdf$System, replacement = "Baseline All-Intervention")
FSdf$System <-str_replace("No PreWash", string = FSdf$System, replacement = "No Prewash")
FSdf$System<-factor(FSdf$System, levels=c("Baseline No-Intervention", "Baseline All-Intervention","No Holding", "No Precooling", "No Prewash", "No Washing", "No Sanitation" ))


hline_data <- data.frame(y = c(0,-3.416,-2.5970,-3.412,-2.1759,-2.12,-3.373), 
System = factor(c("Baseline No-Intervention", "Baseline All-Intervention","No Holding", "No Precooling", "No Prewash", "No Washing", "No Sanitation" ), levels =c("Baseline No-Intervention", "Baseline All-Intervention","No Holding", "No Precooling", "No Prewash", "No Washing", "No Sanitation" ) ), stringsAsFactors = FALSE)

hline_data2 <- data.frame(y = c(-3.416),Baseline_System = factor(c("Baseline")), 
                         stringsAsFactors = FALSE)

FSdf <- FSdf %>% mutate(ints3 = rep(c(0,-3.416,-0.805564771,0.015250639
,-1.250976121,-0.012333977,
-1.320045958
), each =8))


ggplot(data= FSdf, aes(x = fct_reorder(Name, abs(FS)), y = FS, fill = System))+
  geom_col()+
  coord_flip()+
  facet_wrap(~System,scales = "free_y")  +
  ylab("Factor Sensitivity Index")+
  xlab("Processing system + Sampling Plan")+
  geom_hline(data = hline_data, aes(yintercept = y, linetype = System),size =0.7)+
  #geom_hline(data = hline_data2, aes(yintercept = y, linetype = Baseline_System),size =2, color = "red")+
  geom_hline(aes(yintercept = -3.416),size =0.7, color = "red", alpha = 0.5)+
  theme_bw()+
  theme(text = element_text(size=6.5), axis.text = element_text(size = 6))+
  theme(legend.key.size = unit(0.8,"line"))
  #theme(legend.text=element_text(size=20),legend.title=element_text(size=20))
  
  ggsave("Figure 6- Factor Sensitivity.jpeg", width = 6.8, height = 3.7, units = "in", dpi = 300)
  ggsave("Figure 6- Factor Sensitivity.tiff", width = 6.8, height = 3.7, units = "in", dpi = 300)

pfs

```

## Contamination at sampling Point

```{r}
#AI and NOI: This one used fir comparing AI and No

Con_S<-read_csv("ContSamp-Final.csv")
Con_S_AI<-read_csv("ContSamp_AI-Final.csv")

Con_S$Process<-"No Intervetion"
Con_S_AI$Process<-"All Interventions"

####
Con_S %>% 
  group_by(variable) %>% 
  summarise(mean(value), quantile(value, 0.05), quantile(value, 0.95))
  
Con_S_AI %>% 
  group_by(variable) %>% 
  summarise(mean(value), quantile(value, 0.05), quantile(value, 0.95))

Binded_Con<-bind_rows(Con_S,Con_S_AI)


Order_ConS<-unique(Con_S$variable)
Binded_Con$variable<-factor(Binded_Con$variable, levels=Order_ConS)
Binded_Con$`Cont Scenario`<-factor(Binded_Con$`Cont Scenario`, levels=c("Random","10% Cluster","1% Cluster"))

Binded_Con %>% 
  group_by(variable) %>% 
  summarise(mean = mean(value), quantile5 = quantile(value, 0.05),quantile95 = quantile(value, 0.95))

Binded_Con$`Cont Scenario`
Binded_Con$Process<-str_replace("No Intervetion", string = Binded_Con$Process, replacement = "No Interventions")



ggplot(data = Binded_Con, aes(x = variable, y =value, fill = `Cont Scenario`))+
  geom_boxplot()+
   scale_y_continuous(trans='log10',
                      labels = trans_format("log10", math_format(10^.x)))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  theme(text = element_text(size=24), legend.text=element_text(size=18),legend.title=element_text(size=22))+
  labs(x= "Sampling Step", y = "Total Adulterant Cells in System")+
  facet_wrap(~Process)+
  scale_fill_discrete(name = "Contamination Scenario")

ggsave("Cont_Sampling-Final.tiff", width = 40, height = 30, units = "cm", dpi = 600)

#ALL Binded: this used to compared all other interventions Review 2
Cont_Samp_Point_Binded<-read_csv("ContSampPointR2.csv")

Cont_Samp_Point_Binded$`Cont Scenario`<-str_replace("Random Uniform Unclustered", string = Cont_Samp_Point_Binded$`Cont Scenario`, replacement = "Random Uniform (Widespread 100% Cluster)")

Order_ConS<-unique(Cont_Samp_Point_Binded$variable)
Cont_Samp_Point_Binded$variable<-factor(Cont_Samp_Point_Binded$variable, levels=Order_ConS)
Cont_Samp_Point_Binded$`Cont Scenario`<-factor(Cont_Samp_Point_Binded$`Cont Scenario`, levels = c("Random Uniform (Widespread 100% Cluster)", "10% Cluster", "1% Cluster"))
Cont_Samp_Point_Binded$Process<-factor(Cont_Samp_Point_Binded$Process, levels = c("No Intervention","No Holding","No Precooling","No Sanitation", "No Prewash","No Washing" , "All Intervention"))


ggplot(data = Cont_Samp_Point_Binded, aes(x = variable, y =value, fill = `Cont Scenario`))+
  geom_boxplot()+
   scale_y_continuous(trans='log10',
                      labels = trans_format("log10", math_format(10^.x)))+
  labs(x= "Sampling Step", y = "Total Adulterant Cells in System")+
  facet_wrap(~Process)+
  scale_fill_discrete(name = "Contamination Scenario")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  theme(text = element_text(size=24), legend.text=element_text(size=18),legend.title=element_text(size=22))

ggsave("Cont_Sampling Point.tiff", width = 40, height = 30, units = "cm", dpi = 600)
ggsave("Cont_Sampling Point.jpeg", width = 40, height = 30, units = "cm", dpi = 600)

ggplot(data = Cont_Samp_Point_Binded, aes(x = Process, y =value, fill = `Cont Scenario`))+
  geom_boxplot(size = 0.2,outlier.size=0.2)+
   scale_y_continuous(trans='log10',
                      labels = trans_format("log10", math_format(10^.x)))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  theme(text = element_text(size=7))+
  theme(legend.key.size = unit(0.8,"line"))+
  labs(x= "Sampling Step", y = "Total Adulterant Cells in System")+
  facet_wrap(~variable)+
  scale_fill_discrete(name = "Contamination Scenario")

ggsave("Figure S2 - Contamination Samp Points.tiff", width = 6.8, height = 4.5, units = "in", dpi = 300)
ggsave("Figure S2 - Contamination Samp Points.jpeg", width = 6.8, height = 4.5, units = "in", dpi = 300)


Conts_At_SP<- Cont_Samp_Point_Binded %>% 
  group_by(variable, Process) %>% 
  summarise(mean = mean(value), q5 = quantile(value, 0.05), q95 = quantile(value, 0.95)) 

write.csv(Conts_At_SP,file ="Conts_At_SP.csv" )


Conts_SP<- Cont_Samp_Point_Binded %>% 
  group_by(variable, Process,`Cont Scenario`) %>% 
  summarise(mean = mean(value), q5 = quantile(value, 0.05), q95 = quantile(value, 0.95))



X<-split(Conts_SP, Conts_SP$`Cont Scenario`)

write.csv(X[1],file ="Cont1.csv" )
write.csv(X[2],file ="Cont2.csv" )
write.csv(X[3],file ="Cont3.csv" )

```


##Expossure and Prevalence comparison Chart

```{r}

Exposure_Chart<-read_csv("Exposure_Chart_df-Final.csv")
Exposure_Chart<-Exposure_Chart[-1]

Exposure_Chart$Cont_Spread<-str_replace("Random", string = Exposure_Chart$Cont_Spread, replacement = "Random Uniform (Widespread 100% Cluster)")

unique(Exposure_Chart$Cont_Spread)
levels_1<-c("Baseline", "PHS4D", "PHS4H", "PHSInt", "HTrad", "RSTrad", "FPSTrad", "CS")
levels_2<-c("Baseline", "CS", "PHS4D", "HTrad", "RSTrad","PHS4H", "FPSTrad", "PHSInt")

Exposure_Chart$Cont_Spread<-factor(Exposure_Chart$Cont_Spread, levels = c("Random Uniform (Widespread 100% Cluster)", "10% Cluster", "1% Cluster"))


Exposure_Chart<-Exposure_Chart %>% 
  mutate(log10cont = log10(Final_CFU_Acc_Portion_mean),)

#Exposure.
ggplot(data = Exposure_Chart,aes(x = factor(Sampling_Plan, levels =levels_1 ) ,y = MeanComparison, group = Baseline_Scenario,color = Baseline_Scenario))+
  theme_bw()+
  geom_point(size = 4)+
  theme(text = element_text(size=26), axis.text = element_text(size = 24))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=20))+
  #geom_col(data = Exposure_Chart, aes(x =factor(Sampling_Plan, levels =levels_2), y = log10cont))+
  facet_wrap(~Cont_Spread)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(y= "Relative TAC Exposure", x = "Sampling Plan", color= "Baseline Scenario")+
  scale_y_continuous(labels = percent)+
  geom_line(aes(group = Sampling_Plan),
            color="black",
            alpha = 0.7 ,
            arrow = arrow(length=unit(0.3,"cm"), ends="last", type = "closed"))+
  ggtitle("Relative TAC Exposure")+
  geom_hline(aes(yintercept = 0.3040073, linetype = "Maximum effect NI system"), size = 2)+
  geom_hline(aes(yintercept = 0.7794872, linetype = "Maximum effect AI system"), size = 2)+
  scale_linetype_manual(name ="", values = c('dotted','dashed')) 


ggsave("Relative Exposure-Final.tiff", width = 40, height = 28, units = "cm", dpi = 600)

scale_color_manual(values = c("Baseline" = "black", "PHS4D" = "red","PHS4H" = "black","PHSInt" = "black","HTrad" = "black","RSTrad" = "black","FPSTrad" = "black","CS" = "black"))
 
  
#Relative Prevalence
  
ggplot(data = Exposure_Chart,aes(x = factor(Sampling_Plan, levels =levels_1 ) ,y =Prevalence_Comparison, group = Baseline_Scenario,color = Baseline_Scenario))+
  theme_bw()+
  geom_point(size = 4)+
  theme(text = element_text(size=26), axis.text = element_text(size = 24))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=20))+
  #geom_col(data = Exposure_Chart, aes(x =factor(Sampling_Plan, levels =levels_2), y = log10cont))+
  facet_wrap(~Cont_Spread)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(y= "Relative Prevalence of Contaminated Packages", x = "Sampling Plan", color= "Baseline Scenario")+
  scale_y_continuous(labels = percent)+
  geom_line(aes(group = Sampling_Plan),
            color="black",
            alpha = 0.7 ,
            arrow = arrow(length=unit(0.3,"cm"), ends="last", type = "closed"))+
  ggtitle("Relative Prevalence")+
  geom_hline(aes(yintercept = 0.3667362, linetype = "Maximum effect NI system"), size = 2)+
  geom_hline(aes(yintercept = 0.7794872, linetype = "Maximum effect AI system"), size = 2)+
  scale_linetype_manual(name ="", values = c('dotted','dashed')) 

ggsave("Relative Prevalence.tiff", width = 6.8, height = 4.5, units = "in",  dpi = 300)

  
  
#Cont 
  ggplot(data = Exposure_Chart,aes(y = factor(Sampling_Plan, levels =levels_2 ) ,x = log10cont, group = Baseline_Scenario,fill = Baseline_Scenario))+
  theme_bw()+
  geom_col(position = "dodge")+
  #geom_point(size = 2.5)+
  #geom_col(data = Exposure_Chart, aes(x =factor(Sampling_Plan, levels =levels_2), y = log10cont))+
  facet_wrap(~Cont_Spread)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(y= "Log10 Total Cells Exposure", x = "Sampling Plan", color= "Baseline Scenario")+
  #scale_y_continuous(labels = percent)+
  #geom_line(aes(group = Sampling_Plan),
            #color="black",
            #alpha = 0.7 ,
            #arrow = arrow(length=unit(0.15,"cm"), ends="first", type = "closed"))+
  ggtitle("Total Cells Exposure")
  


```


#Exposure Comparison with more in between scenarios

```{r}
Exposure_Chart<-read_csv("Exposure_Chart_df-FinalR2.csv")
Exposure_Chart<-Exposure_Chart[-1]

Exposure_Chart$MeanComparison = 1-Exposure_Chart$MeanComparison

unique(Exposure_Chart$Cont_Spread)
levels_1<-c("Baseline", "PHS4D", "PHS4H", "PHSInt", "HTrad", "RSTrad", "FPSTrad", "CS")
levels_2<-c("Baseline", "CS", "PHS4D", "HTrad", "RSTrad","PHS4H", "FPSTrad", "PHSInt")

Exposure_Chart$Cont_Spread<-str_replace("Random Uniform Unclustered", string = Exposure_Chart$Cont_Spread, replacement = "Random Uniform (Widespread 100% Cluster)")

Exposure_Chart$Cont_Spread<-factor(Exposure_Chart$Cont_Spread, levels = c("Random Uniform (Widespread 100% Cluster)", "10% Cluster", "1% Cluster"))


Exposure_Chart<-Exposure_Chart %>% 
  mutate(log10cont = log10(Final_CFU_Acc_Portion_mean))

Exposure_Chart$Baseline_Scenario<-str_replace("All Intervention", string = Exposure_Chart$Baseline_Scenario, replacement = "Baseline All-Intervention")
Exposure_Chart$Baseline_Scenario<-str_replace("No Intervention", string = Exposure_Chart$Baseline_Scenario, replacement = "Baseline No-Intervention")


Exposure_Chart$Baseline_Scenario<-factor(Exposure_Chart$Baseline_Scenario, levels=c("Baseline No-Intervention", "Baseline All-Intervention","No Holding", "No Precooling", "No Prewash", "No Washing", "No Sanitation" ))

#Exposure.
ggplot(data = Exposure_Chart,aes(x = factor(Sampling_Plan, levels =levels_1 ) ,y = MeanComparison, group = Baseline_Scenario,fill = Baseline_Scenario))+
  theme_bw()+
  geom_line(aes(color =Baseline_Scenario), size  =0.7, alpha = 0.5)+
  geom_point(size = 2, position = position_dodge(width = 0),shape = 21, alpha = 1)+
  #theme(text = element_text(size=26), axis.text = element_text(size = 24))+
  #theme(legend.text=element_text(size=16),legend.title=element_text(size=20))+
  #geom_col(data = Exposure_Chart, aes(x =factor(Sampling_Plan, levels =levels_2), y = log10cont))+
  facet_wrap(~Cont_Spread)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(y= "Relative Efficacy: Endpoint TAC", x = "Sampling Plan", color= "Process System", fill = "Process System")+
  scale_y_continuous(labels = percent)+
  theme(text = element_text(size=7))+
  theme(legend.key.size = unit(0.8,"line"))


ggsave("Figure 5 - Efficacy.tiff", width = 6.8, height = 3.7, units = "in", dpi = 300)
ggsave("Figure 5 - Efficacy.jpeg", width = 6.8, height = 3.7, units = "in", dpi = 300)



ggplot(data = Exposure_Chart,aes(x = factor(Sampling_Plan, levels =levels_1 ) ,y = MeanComparison, group = Cont_Spread,fill = Cont_Spread))+
  geom_col(position = position_dodge2())+
  theme_bw()+
  facet_wrap(~Baseline_Scenario)
  

```




## Poster Plot Scenario Comparison CPS Symp 2022 

this got replaced by the Factor Sensitivity plot later on. 
```{r}
order_x2 = c('BaselineNI',
 'PHS4D_NI',
 'PHS4H_NI',
 'PHSInt_NI',
 'HTrad_NI',
 'RSTrad_NI',
 'FPSTrad_NI',
 'CS_NI',
 'BaselineAI',
 'PHS4D_AI',
 'PHS4H_AI',
 'PHSInt_AI',
 'HTrad_AI',
 'RSTrad_AI',
 'FPSTrad_AI',
 'CS_AI')

labels_2 = c('BaselineNI' = "Baseline",
 'PHS4D_NI'= "PHS 4d",
 'PHS4H_NI'= "PHS 4h",
 'PHSInt_NI'= "PHS Int",
 'HTrad_NI'= "HS",
 'RSTrad_NI'= "RS",
 'FPSTrad_NI'= "FPS",
 'CS_NI'= "CS",
 'BaselineAI'= "Baseline",
 'PHS4D_AI'= "PHS 4d",
 'PHS4H_AI'= "PHS 4h",
 'PHSInt_AI'= "PHS Int",
 'HTrad_AI'= "HS",
 'RSTrad_AI'= "RS",
 'FPSTrad_AI'= "FPS",
 'CS_AI'= "CS")




Final_Exps<-read_csv("final_exp.csv")
empty<-c()
list_loop<-c(1,9,17,25,33,41)
for (i in list_loop ){
  list_2<-Final_Exps$Expossure[i:(i+7)]/Final_Exps$Expossure[i]
  empty<-c(empty,list_2 )
}

Final_Exps$`Relative Difference`<-empty

Final_Exps[48,6] = 0.999999
Final_Exps[32,6] = 0.999999

Final_Exps$`Sampling Plan`<-factor(Final_Exps$`Sampling Plan`, levels = order_x2)
Final_Exps$`Cont Scenario`<-factor(Final_Exps$`Cont Scenario`, levels = c("Random Contamination", "10% Cluster Contamination",  "1% Cluster Contamination"))

ggplot(data= Final_Exps, aes(x =fct_reorder(`Sampling Plan`, `Relative Difference`) , y = `Relative Difference`, fill =`Cont Scenario` ))+
  geom_col(position = "dodge")+
  coord_flip()+
  theme(text = element_text(size=26), axis.text = element_text(size = 24))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=20))+
  geom_hline(yintercept = 1,linetype="dashed",size = 2)+
  labs(x= "Sampling Plan", y= "Relative Difference: Total Consumer Exposure")+
  facet_wrap(.~ `Baseline System`, scales = "free")+
  theme(legend.position = 'top', 
        legend.spacing.x = unit(1.0, 'cm'))+
  scale_x_discrete(labels = labels_2)+
  scale_y_continuous(labels = scales::percent)
  #geom_hline(yintercept = 13740302,linetype="dotted")+
  #geom_hline(yintercept = 4532,linetype="dashed")
  #ggsave("EXposure-Final.png", width = 40, height = 28, units = "cm", dpi = 600)
```





